### 2008-12-15 doc/sec/ManualofSecurityFramework.tex
some changes in documentation

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{supertabular}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% Text styles
\newcommand\textstyleInternetlink[1]{\textcolor[rgb]{0.0,0.0,0.5019608}{#1}}
% Outline numbering
\setcounter{secnumdepth}{3}
\renewcommand\thesection{\arabic{section}.}
\renewcommand\thesubsection{\arabic{subsection}.}
\renewcommand\thesubsubsection{\arabic{subsection}.\arabic{subsubsection}.}
\makeatletter
\newcommand\arraybslash{\let\\\@arraycr}
\makeatother
% List styles
\newcounter{saveenum}
\newcommand\liststyleWWviiiNumxi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumxv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxvi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxxiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.2673in}
\setlength\paperheight{11.6925in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{1in}
\setlength\oddsidemargin{1.25in}
\setlength\textheight{9.0315in}
\setlength\textwidth{5.7672997in}
\setlength\footskip{0.661in}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Convertv{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{\thepage{}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\newcounter{Bibitem}
\renewcommand\theBibitem{\arabic{Bibitem}}
\title{}
\begin{document}
\begin{flushleft}
\tablehead{}\begin{supertabular}{m{1.3809599in}m{2.0976598in}}
\begin{center}
\includegraphics[width=1.422in,height=0.9091in]{ManualofSecurityFramework-img1.jpg}
\end{center}
 &
\selectlanguage{english}\scshape\color{black} \newline
\newline
NORDUGRID\\
\end{supertabular}
\end{flushleft}

@@

\subsubsection{SP Service and SAML2SSO Service Provider Handler}
{\selectlanguage{english}\color{black}
Service Provider servicer (SP service) implements the functionality of
Service Provider in SAML2 Web SSO profile. }

{\selectlanguage{english}\color{black}
Normally SP service will not be deployed independently, instead, it
should be deployed together with other services. The SLCS service is
the typical deployment about SP service. On the client side, client
developer should use the ClientSAML2Interface instead of
ClientInterface to call the client functionality. The SLCS client
(arcslcs) is the typical usage of \ ClientSAML2Interface.}

{\selectlanguage{english}\color{black}
Once the SP Service has cooperated with user agent and Identity Provider
(external) and succeeded to accomplish the SAML2 SSO profile, \ the SP
service will get the saml authentication assertion which asserts that
the authentication has succeeded, and then SP service will store this
assertion into session context.}

{\selectlanguage{english}\color{black}
SAML2 service provider handler (saml2ssoserviceprovider.handler) is the
security handler which will understand the authentication assertion and
make authorization decision according to this assertion.}

{\selectlanguage{english}\color{black}
The example configuration about using SP service and SAML2SSO service
provider handler can be seen in the configuration of SLCS service. }

{\selectlanguage{english}\color{black}
SP service is not only supposed to work together with SLCS service. But
if it is used to work together with other services, the client should
be developed on \ ClientSAML2Interface instead of ClientInterface.}

\subsubsection{SLCS service and client}
{\selectlanguage{english}\color{black}
Short-lived credential service (SLCS) is for signing short-lived x509
credential for user based user{\textquotesingle}s username/password
credential. Then the user can use the short-lived x509 credential to
access grid services/resources where x509 credential is required by
default. \ SLCS service should depend on the SP (Service provider)
service which is one of the participants of SAML2 SSO profile (SAML2
SSO profile is used for authenticating based on username/password
credential and getting SAML authentication assertion; and SAML
authentication assertion is then used as basis for signing short-lived
x509 credential).}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}SecHandler
name={\textquotedbl}\textcolor[rgb]{0.8627451,0.13725491,0.0}{saml2ssoserviceprovider.handler}{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}

@@

{\selectlanguage{english}\color{black}
SLCS service and SP service should together be configured by using the
Plexer. SP service is directly based on http and SLCS is directly based
on soap. }

{\selectlanguage{english}\color{black}
SLCS service should specifically include the CA credential (certificate
and key file) and the serial number file (which includes the serial
number of each signed certificate).}

@@

{\selectlanguage{english}\color{black}
\ \ {}-D, -{}-storedir=directory \ \ \ \ Store directory for key and
signed certificate }

@@

{\selectlanguage{english}\color{black}
Note user should input the {\textquotedblleft}IdP
name{\textquotedblright} is the corresponding Identity Provider (one of
the participants of SAML2 SSO profile) name to which the user would
authentication against by using its username/password credential. And
the name is stored inside the metadata on both SP service and IdP
provider, and it is used by SP service to get the authentication URL
for username/password based authentication.}

{\selectlanguage{english}\color{black}
And the {\textquotedblleft}user{\textquotedblright} and
{\textquotedblleft}password{\textquotedblright} is the credential which
will be used to authentication against IdP.}

@@

\clearpage{\centering\selectlanguage{english}\bfseries\scshape\color{black}
References
\par}

{\selectlanguage{english}\color{black}
\stepcounter{Bibitem}{\theBibitem}. RFC3820- Internet X.509 Public Key
Infrastracture (PKI) Proxy, \url{http://rfc.net/rfc3820.html}}

{\selectlanguage{english}\color{black}
\stepcounter{Bibitem}{\theBibitem}. D1.2-2 The ARC container (first
prototype),
\url{http://www.knowarc.eu/documents/Knowarc_D1.2-2_07.pdf}}

{\selectlanguage{english}\color{black}
\textstyleInternetlink{\textcolor{black}{\stepcounter{Bibitem}{\theBibitem}}}\textstyleInternetlink{\textcolor{black}{.}}\textstyleInternetlink{\foreignlanguage{english}{\textcolor{black}{Web
Service Security Username Token Profile 1.1.
}}}\url{http://www.oasis-open.org/committees/download.php/16782/wss-v1.1-spec-os-UsernameTokenProfile.pdf}}

{\selectlanguage{english}\color{black}
\stepcounter{Bibitem}{\theBibitem}. OGSA{\textregistered} Basic
Execution Service Version 1.0,
\ \url{http://www.ogf.org/documents/GFD.108.pdf} }

{\selectlanguage{english}\color{black}
\textstyleInternetlink{\textcolor{black}{\stepcounter{Bibitem}{\theBibitem}}}\textstyleInternetlink{\textcolor{black}{.
OASIS Web Services Security (WSS) TC.
}}\url{http://www.oasis-open.org/committees/tc_home.php?wg_abbrev=wss}}
\end{document}

>>>>

% This file was converted to LaTeX by Writer2LaTeX ver. 0.5
% see http://www.hj-gym.dk/~hj/writer2latex for more info
\documentclass{article}
\usepackage[ascii]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amssymb,amsfonts,textcomp}
\usepackage{color}
\usepackage{array}
\usepackage{supertabular}
\usepackage{hhline}
\usepackage{hyperref}
\hypersetup{pdftex, colorlinks=true, linkcolor=blue, citecolor=blue, filecolor=blue, pagecolor=blue, urlcolor=blue, pdftitle=, pdfauthor=qiangwz, pdfsubject=, pdfkeywords=}
\usepackage[pdftex]{graphicx}
% Outline numbering
\setcounter{secnumdepth}{3}
\renewcommand\thesection{\arabic{section}.}
\renewcommand\thesubsection{\arabic{subsection}.}
\renewcommand\thesubsubsection{\arabic{subsection}.\arabic{subsubsection}.}
\makeatletter
\newcommand\arraybslash{\let\\\@arraycr}
\makeatother
% List styles
\newcounter{saveenum}
\newcommand\liststyleWWviiiNumxi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxii{%
\renewcommand\labelitemi{[F0B7?]}
\renewcommand\labelitemii{[F0B7?]}
\renewcommand\labelitemiii{[F0B7?]}
\renewcommand\labelitemiv{[F0B7?]}
}
\newcommand\liststyleWWviiiNumxv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxvi{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
\newcommand\liststyleWWviiiNumxxiv{%
\renewcommand\theenumi{\arabic{enumi}}
\renewcommand\theenumii{\arabic{enumii}}
\renewcommand\theenumiii{\arabic{enumiii}}
\renewcommand\theenumiv{\arabic{enumiv}}
\renewcommand\labelenumi{\theenumi.}
\renewcommand\labelenumii{\theenumii.}
\renewcommand\labelenumiii{\theenumiii.}
\renewcommand\labelenumiv{\theenumiv.}
}
% Page layout (geometry)
\setlength\paperwidth{8.2673in}
\setlength\paperheight{11.6925in}
\setlength\voffset{-1in}
\setlength\hoffset{-1in}
\setlength\topmargin{1in}
\setlength\oddsidemargin{1.25in}
\setlength\textheight{9.0315in}
\setlength\textwidth{5.7672997in}
\setlength\footskip{0.661in}
\setlength\headheight{0cm}
\setlength\headsep{0cm}
% Footnote rule
\setlength{\skip\footins}{0.0469in}
\renewcommand\footnoterule{\vspace*{-0.0071in}\setlength\leftskip{0pt}\setlength\rightskip{0pt plus 1fil}\noindent\textcolor{black}{\rule{0.25\columnwidth}{0.0071in}}\vspace*{0.0398in}}
% Pages styles
\makeatletter
\newcommand\ps@Convertv{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\newcommand\ps@Standard{
  \renewcommand\@oddhead{}
  \renewcommand\@evenhead{}
  \renewcommand\@oddfoot{\thepage{}}
  \renewcommand\@evenfoot{\@oddfoot}
  \renewcommand\thepage{\arabic{page}}
}
\makeatother
\pagestyle{Standard}
\setlength\tabcolsep{1mm}
\renewcommand\arraystretch{1.3}
\title{}
\begin{document}
\begin{flushleft}
\tablehead{}\begin{supertabular}{m{1.3809599in}m{2.0976598in}}
\begin{center}
\includegraphics[width=1.422in,height=0.9091in]{ManualofSecurityFramework-img1.jpg}
\end{center}
 &
\selectlanguage{english}\scshape\color{black} \newline
\newline
NORDUGRID\\
\end{supertabular}
\end{flushleft}

@@

\subsubsection{SP Service and SAML2SSO Service Provider Handler}
{\selectlanguage{english}\color{black}
\ \ \ \ Service Provider servicer (SP service) implements the
functionality of Service Provider in SAML2 Web SSO profile.}

{\selectlanguage{english}\color{black}
\ \ \ \ Normally SP service will not be deployed independently, instead,
it should be deployed together with other services. The SLCS service is
the typical deployment about SP service. On the client side, client
developer should use the ClientSAML2Interface instead of
ClientInterface to call the client functionality. The SLCS client
(arcslcs) is the typical usage of \ ClientSAML2Interface.}

{\selectlanguage{english}\color{black}
\ \ \ \ Once the SP Service has cooperated with user agent and Identity
Provider (external) and succeeded to accomplish the SAML2 SSO profile,
\ the SP service will get the saml authentication assertion which
asserts that the authentication has succeeded, and then SP service will
store this assertion into session context.}

{\selectlanguage{english}\color{black}
\ \ \ \ SAML2 assertion consumer handler
(saml2ssoassertionconsumer.handler) is the security handler which will
understand the authentication assertion and attribute assertion from
IdP, and make authorization decision according to the attribute values
inside these assertions. Currently the SAML2 assertion consumer handler
is an empty security handler and does not effect the services.}

{\selectlanguage{english}\color{black}
\ \ \ \ The example configuration about using SP service and SAML2SSO
assertion consumer handler can be seen in the configuration of SLCS
service. }

{\selectlanguage{english}\color{black}
\ \ \ \ SP service is not only supposed to work together with SLCS
service. If it is used to work together with other services, the client
should be developed on ClientSAML2Interface instead of ClientInterface,
which is the same as that in SLCS client (\textit{arcslcs}).}

\subsubsection{SLCS service and client}
{\selectlanguage{english}\color{black}
\ \ \ \ Short-lived credential service (SLCS) is for signing short-lived
x509 credential for user based user{\textquotesingle}s
username/password credential. Then the user can use the short-lived
x509 credential to access grid services/resources where x509 credential
is required by default. \ SLCS service should depend on the SP (Service
provider) service which is one of the participants of SAML2 SSO profile
(SAML2 SSO profile is used for authenticating based on
username/password credential and getting SAML authentication assertion;
and SAML authentication assertion is then used as basis for signing
short-lived x509 credential).}

@@

{\selectlanguage{english}\ttfamily\color{black}
\ \ \ \ {\textless}SecHandler
name={\textquotedbl}\textcolor[rgb]{0.8627451,0.13725491,0.0}{saml2ssoassertionconsumer.handler}{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ SLCS service and SP service should together be configured by
using the Plexer. SP service is directly based on http and SLCS is
directly based on soap. }

{\selectlanguage{english}\color{black}
\ \ \ \ SLCS service should specifically include the CA credential
(certificate and key file) and the serial number file (which includes
the serial number of each signed certificate). Therefore, the service
administrator should firstly create a CA credential (note for
interoperability purpose in the production grid deployment, the CA
credential should be trusted by others). }

@@

{\selectlanguage{english}\color{black}
\ \ {}-D, -{}-storedir=directory \ \ \ \ Store directory for key and
signed certificate}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ Note user should input the {\textquotedblleft}IdP
name{\textquotedblright} is the corresponding Identity Provider (one of
the participants of SAML2 SSO profile) name to which the user would
authenticate against by using its username/password credential. And the
name is stored inside the metadata on both SP service and IdP provider,
and it is used by SP service to get the authentication URL for
username/password based authentication.}

{\selectlanguage{english}\color{black}
\ \ \ \ And the {\textquotedblleft}user{\textquotedblright} and
{\textquotedblleft}password{\textquotedblright} is the credential which
will be used to authentication against IdP.}

@@

{\selectlanguage{english}\color{black}
\ \ \ \ There is a temporary Identity Provider (IdP) deployed on
\textit{squark.uio.no} for test with the following test username and
password: staff, researcher, librarian, binduser; with the same
password {\textquotedbl}123456{\textquotedbl}}

{\selectlanguage{english}\color{black}
./arcslcs -S https://127.0.0.1:60000/slcs -I
https://squark.uio.no/idp/shibboleth -U staff -P 123456 -D
/home/wzqiang/arc-0.9/src/clients/credentials -c client.xml}

{\selectlanguage{english}\upshape\color{black}
\ \ \ \ The short-lived credential issued by SLCS service will include
the SAML assertion as the extension of X.509 certificate as a proof of
passing SAML2 SSO profile.}
\end{document}

### 2008-12-15 doc/sec/SecurityFrameworkofARC1.tex
some changes in documentation

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}saml2ssoserviceprovider.handler{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}

>>>>

{\selectlanguage{english}\itshape\color{black}
\ \ \ \ \ \ \ \ \ \ \ \ {\textless}SecHandler
name={\textquotedbl}saml2ssoassertionconsumer.handler{\textquotedbl}
id={\textquotedbl}saml2ssosp{\textquotedbl}
event={\textquotedbl}incoming{\textquotedbl}/{\textgreater}}
